### 2022-10-10 doc/manuscript/translocation.qmd
Add additional references and comments to framing

---
format: docx
editor: visual
csl: science.csl
bibliography: translocation.bib
reference-doc: translocation_style_ref.docx
---

@@

-   Species recovery in the face of disease will depend the ability of a species to move or change.

@@

-   **Potential knowledge gap**: Subsequent recoveries from disease-induced declines following observed genetic changes have rarely [never?] been documented in wildlife populations.

@@

>>>>

---
format: docx
editor: visual
csl: science.csl
bibliography: translocation.bib
---

@@

-   Species recovery in the face of disease will depend on the ability of a species to move or change.

@@

-   **Potential knowledge gap**: Subsequent recoveries from disease-induced declines following observed genetic changes have rarely \[never?\]
    been documented in wildlife populations (Sea stars: Moritsch and Raimondi 2018?).

@@

[This is excellent. Thanks for adding it.]: #
